My title\thanks{Code and data are available at: LINK.}

### 2024-02-08 paper/paper.qmd
making it even uglier

```{r}
ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species),
             size = 10,
             alpha = 1) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species",
    shape = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.7),
    plot.title.position = "plot",
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )

>>>>

```{r}
ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species, shape = sex),
             size = 10,
             alpha = 1) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.9),
    plot.title.position = "plot",
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )

### 2024-02-08 paper/paper.tex
making it even uglier

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ penguins,}
       \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ flipper\_length\_mm,}
           \AttributeTok{y =}\NormalTok{ body\_mass\_g)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{color =}\NormalTok{ species),}
             \AttributeTok{size =} \DecValTok{10}\NormalTok{,}
             \AttributeTok{alpha =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{"red"}\NormalTok{, }\StringTok{"pink"}\NormalTok{, }\StringTok{"red"}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Penguins are mean, ur mom\textquotesingle{}s house"}\NormalTok{,}
    \AttributeTok{subtitle =} \StringTok{"Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Flipper length (houses)"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Body mass (bluberries)"}\NormalTok{,}
    \AttributeTok{color =} \StringTok{"Penguin species"}\NormalTok{,}
    \AttributeTok{shape =} \StringTok{"Penguin species"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}
    \AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.7}\NormalTok{),}
    \AttributeTok{plot.title.position =} \StringTok{"plot"}\NormalTok{,}
    \AttributeTok{plot.caption =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{hjust =} \DecValTok{0}\NormalTok{, }\AttributeTok{face =} \StringTok{"italic"}\NormalTok{),}
    \AttributeTok{plot.caption.position =} \StringTok{"plot"}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 2 rows containing missing values (`geom_point()`).
\end{verbatim}

>>>>

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, sharp corners, enhanced, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ penguins,}
       \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ flipper\_length\_mm,}
           \AttributeTok{y =}\NormalTok{ body\_mass\_g)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{color =}\NormalTok{ species, }\AttributeTok{shape =}\NormalTok{ sex),}
             \AttributeTok{size =} \DecValTok{10}\NormalTok{,}
             \AttributeTok{alpha =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{"red"}\NormalTok{, }\StringTok{"pink"}\NormalTok{, }\StringTok{"red"}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Penguins are mean, ur mom\textquotesingle{}s house"}\NormalTok{,}
    \AttributeTok{subtitle =} \StringTok{"Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Flipper length (houses)"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Body mass (bluberries)"}\NormalTok{,}
    \AttributeTok{color =} \StringTok{"Penguin species"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}
    \AttributeTok{legend.position =} \FunctionTok{c}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\FloatTok{0.9}\NormalTok{),}
    \AttributeTok{plot.title.position =} \StringTok{"plot"}\NormalTok{,}
    \AttributeTok{plot.caption =} \FunctionTok{element\_text}\NormalTok{(}\AttributeTok{hjust =} \DecValTok{0}\NormalTok{, }\AttributeTok{face =} \StringTok{"italic"}\NormalTok{),}
    \AttributeTok{plot.caption.position =} \StringTok{"plot"}
\NormalTok{  )}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: Removed 11 rows containing missing values (`geom_point()`).
\end{verbatim}
